---
output: 
  github_document:
    toc: TRUE
    toc_depth: 2
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = T,
  error = T
)
```

# *To the reader*

Welcome to the R package building helper *readme2pkg.template.lite*!

Below, is a readme that provides steps for building a package.  This readme acts as a worksheet, checklist, and control document as functions used in package building are included within and can be used in advancing development.

We'll use the `{knitrExtra}` helper package to send code chunks to different directories in the package.

To install `{knitrExtra}`:

```

remotes::install_github("EvaMaeRey/knitrExtra")

```



# Part 00. Proposal

*Note: This README walks through package rational and contains the code that defines proposed package functions and in addition to first-cut testing. [TLDR - Jump to traditional readme content](#traditional-readme)*

Proposing the {xxxx} package! 🦄 
<!-- (typical package introduction write up; but actually aspirational) -->

The goal of {xxxx} is to make ... easier.


Without the package, we live in the effort-ful world that follows 🏋:

```{r}
x <- 4

2*x

```

  
With the {xxxx} package, we'll live in a different world (🦄 🦄 🦄) where the task is a snap 🫰: 

Proposed API:

<!-- The following is fenced off to quote the code, but won't execute.  -->

```

library(xxxxx)

xxxxx::times_two(x = 4)

```

# Part 0. Lay out package infrastructure

```{r, eval = F}
devtools::create(".")
```

# Part I. Work on functionality  🚧 ✅ 

Here is a function that will do some work...


```{r geom_green_histogram}
geom_green_histogram <- function(...){
  
  ggplot2::geom_histogram(fill = "green", ...)
  
}
```


## Try it out

```{r}
library(ggplot2)

ggplot(data = cars) + 
  aes(speed) + 
  geom_green_histogram()
```



# Part II. Packaging and documentation  🚧 ✅ 

## Phase 1. Minimal working package

To build a minimal working package, 1) we'll need to document dependencies 2) send functions to .R files in the R folder, 3) do a package check (this will A. Document our functions and B. this will help us identify problems - for example if we've failed to declare a dependency) and 4) install the package locally.  

Then we'll write up a quick advertisement for what our package is able to do in the 'traditional readme' section.  This gives us a chance to test out the package.

```{r}
### Bit 2a: in the function(s) you wrote above make sure dependencies to functions using '::' syntax to pkg functions 
usethis::use_package("ggplot2") # Bit 2b: document dependencies, w hypothetical ggplot2
```

```{r}
# Bit 3: send the code chunk with function to R folder
knitrExtra:::chunk_to_r(chunk_name = "geom_green_histogram") 
```





```{r, results = "hide"}
# Bit 4: document functions and check that package is minimally viable
devtools::check(pkg = ".")  

# Bit 5: install package locally
devtools::install(pkg = ".", upgrade = "never") 
```




# Traditional README

### Bit 7. 

Write traditional README that uses built package (also serves as a test of build). 🚧 ✅ 

The goal of the {xxxx} package is to ...

Install package with:

```
remotes::install_github("GithubCoolUser/mypacakge")
```

Once functions are exported you can remove go to two colons, and when things are are really finalized, then go without colons (and rearrange your readme...)

```{r, eval = F}
library(mypackage)  ##<< change to your package name here
mypackage:::times_two(10)
```


```{r files-report-and-stop-knit, eval = T}
# for quick knit (exiting early) change eval to TRUE
fs::dir_tree(recurse = T)
knitr::knit_exit()
```


# Bit 8: Compile readme

# Bit 9: Push to github (if your package is connected)

# Bit 10: listen and iterate

## Phase 3: Settling and testing 🚧 ✅ 

### Bit A. Added a description and author information in the [DESCRIPTION file](https://r-pkgs.org/description.html) 🚧 ✅

### Bit B. Added [roxygen skeleton](https://r-pkgs.org/man.html) for exported functions. 🚧 ✅

### Bit D. Settle on [examples](https://r-pkgs.org/man.html#sec-man-examples).  Put them in the roxygen skeleton and readme. 🚧 ✅

### Bit C. Chosen a [license](https://r-pkgs.org/license.html)? 🚧 ✅

```{r, eval = F}
usethis::use_mit_license()
```

### Bit D. Use life-cycle badge

```{r, eval = F}
usethis::use_lifecycle_badge("experimental") 
```


### Bit E. Written formal [tests](https://r-pkgs.org/testing-basics.html) of functions and save to test that folders 🚧 ✅




That would look like this...

```{r test_calc_times_two_works, eval = F}
library(testthat)

test_that("calc times 2 works", {
  expect_equal(times_two(4), 8)
  expect_equal(times_two(5), 10)
  
})
```


```{r, eval = F}
knitrExtra::chunk_to_tests_testthat("test_calc_times_two_works")
```




### Bit F. Check again. Addressed notes, warnings and errors. 🚧 ✅


```{r, eval = F}
devtools::check(pkg = ".")
```

## Phase 4. Promote to wider audience...  🚧 ✅ 

### Bit A. Package website built? 🚧 ✅


### Bit B. Package website deployed? 🚧 ✅

## Phase 5: Harden/commit: Submit to CRAN/RUniverse 🚧 ✅ 

# Appendix: Reports, Environment

## Description file complete?  🚧 ✅

```{r, eval = F}
readLines("DESCRIPTION")
```

## Environment  🚧 ✅

Here I just want to print the packages and the versions

```{r}
all <- sessionInfo() |> print() |> capture.output()
all[11:17]
```

## `devtools::check()` report

```{r, eval=F, error = T, results="hide", warning=F}
devtools::check(pkg = ".")
```

## Package directory file tree

```{r}
fs::dir_tree(recurse = T)
```



